---
title: "Baseline characteristics"
format: 
  html:
    toc: true
    toc-depth: 4
editor: visual
execute:
  echo: false
  warning: false
---


```{r}
#| file: R/basic_functions_pkgs.R
```


```{r}
# read in data from data/ folder
tmp <- read_excel("data/Merged_Baseline_and_1_month_Data_4_26_24_note_as_of_4_26_393_completed_1mo_all_393_in_here_v2.xlsx", sheet = 1)

# ?read_excel

# tmp |>
#   select(
#     study_id, contains("date")
#   )
# 
# nrow(tmp)

# screening_survey_timestamp x
# baseline_survey_timestamp
# Date all future weekly emails is based on
# Date 1st weekly email was sent x
# first time clicked on email link

orb <- read_excel("data/data file orbita final.xlsx", sheet = 1,
                  col_names= c("study_id", NA, NA, "domain_id", "page_num", "click_time"),
                  skip = 1) |> 
  select(study_id, domain_id, page_num, click_time)

# orb |> 
#   count(study_id)

# warnings()
```

```{r}

# get the time of first click and
# left join with tmp
# and compute difference bt baseline_survey_timestamp and first_click

# tmp1 <- orb |> 
#   group_by(study_id) |> 
#   summarize(first_click = min(click_time, na.rm =TRUE)) |>
#   right_join(tmp, by = "study_id") |>
#   mutate(
#     time_to_first_click = as.numeric(difftime(first_click, baseline_survey_timestamp, units = "days"))
#   ) |> 
#   select(study_id, baseline_survey_timestamp, first_click, time_to_first_click, rand_round_2)


# summarize the time_to_first_click by rand_round_2
# using tbl_summary()
# compute both median and mean

# tmp1 |> 
#   tbl_summary(by = rand_round_2,
#               include = time_to_first_click,
#               type = all_continuous() ~ "continuous2",
#               statistic = all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})")
#   )

# ?tbl_summary

# tmp1 |> 
  # count(rand_round_2)


# plot the distribution of time_to_first_click by randomization status
# using both boxplot and scatterplot

# tmp1 |> 
#   ggplot(aes(x = factor(rand_round_2), y = time_to_first_click)) +
#   # geom_boxplot() +
#   geom_jitter(width = 0.2, alpha = 0.5) +
#   labs(
#        x = "Randomization status",
#        y = "Time to first click (days)") +
#   theme_minimal() +
#   scale_x_discrete(labels = c("Control", "Tailored")) +
#   theme(
#     panel.grid.major.x = element_blank()
#   )


# create baseline data




```

### Demographics and health information

Patient demographics, health status, medical and surgical histories at baseline (Sec. 5 of `baseline_survey`) are summarized in @tbl-demo.

```{r}
#| label: tbl-demo
#| tbl-cap: Patient demographics and health information by randomized arm.


armfmt <- c("1" = "Control", "2" = "Tailored")
ynfmt <- c("1" = "Yes", "2" = "No", "3" = NA, "99" = NA)



## hisp
# 1 Hispanic/Latino
# 2 Non-Hispanic
# 3 Do not wish to provide
hispfmt <- c("1" = "Hispanic/Latino", "2" = "Non-Hispanic", "3" = "Do not wish to provide")


# 1	ss_eligible_race___1	American Indian or Alaska Native
# 2	ss_eligible_race___2	Asian or Asian American
# 3	ss_eligible_race___3	Black or African American
# 4	ss_eligible_race___4	Native Hawaiian or Pacific Islander
# 5	ss_eligible_race___5	White
# 6	ss_eligible_race___6	Other
# 7	ss_eligible_race___7	Do not wish to provide

racefmt <- c(
  "1" = "American Indian or Alaska Native",
  "2" = "Asian or Asian American",
  "3" = "Black or African American",
  "4" = "Native Hawaiian or Pacific Islander",
  "5" = "White",
  "6" = "Other/More than one",
  "7" = "Do not wish to provide"
)

# 1	8th grade or lower
# 2	Some high school
# 3	High school diploma or GED
# 4	Vocational school or other specialized training
# 5	Some college
# 6	College degree (Associate's or Bachelor's)
# 7	Master's or Doctorate degree
# 8	Do not wish to provide

edufmt <- c(
  "1" = "8th grade or lower",
  "2" = "Some high school",
  "3" = "High school diploma or GED",
  "4" = "Vocational school or other specialized training",
  "5" = "Some college",
  "6" = "College degree (Associate's or Bachelor's)",
  "7" = "Master's or Doctorate degree",
  "8" = "Do not wish to provide"
)

# 0	Retired
# 1	Not working due to a disability
# 2	Not working for another reason
# 3	Stay at home parent or caregiver
# 4	Working full-time
# 5	Working part-time
# 6	Looking for work
# 99	Choose not to answer

workfmt <- c(
  "0" = "Retired",
  "1" = "Not working due to a disability",
  "2" = "Not working for another reason",
  "3" = "Stay at home parent or caregiver",
  "4" = "Working full-time",
  "5" = "Working part-time",
  "6" = "Looking for work",
  "99" = "Choose not to answer"
)

# 1 Excellent
# 2 Very good
# 3 Good
# 4 Fair
# 5 Poor
# 6 Very poor
# 99 Choose not to answer

hlth4fmt <- c(
  "1" = "Excellent",
  "2" = "Very good",
  "3" = "Good",
  "4" = "Fair",
  "5" = "Poor",
  "6" = "Very poor",
  "99" = "Choose not to answer"
)

# demographic data

tmp1 <- tmp |> 
  select(
    study_id, rand_round_2, baseline_survey_timestamp, ss_age, ss_sex, contains("ss_eligible_race"), ss_eligible_hisp,
    ss_eligible_gender, ss_eligible_edu, work_status_bl, height_bl, weight_bl,
    pcp_bl, contains("type_of_insurance_bl"),  pregnancies_bl,
    sf_q1_bl, # overall health,
    contains("medcond_bl"), contains("relevantsurghx_bl") 
    
  )

# View(tmp1)

# tmp1 |> 
#   count(height_bl == 34)
# tmp1 |> 
#   mutate(
#     mm = type_of_insurance_bl___1 + type_of_insurance_bl___2,
#     .after = study_id
#   ) |> 
#   filter(
#     mm > 1
#   )

tmp2 <- tmp1 |> 
  mutate(
    trt = refmt(rand_round_2, armfmt),
    race = case_when(
      ss_eligible_race___1 == 1 ~ 1,
      ss_eligible_race___2 == 1 ~ 2,
      ss_eligible_race___3 == 1 ~ 3,
      ss_eligible_race___4 == 1 ~ 4,
      ss_eligible_race___5 == 1 ~ 5,
      ss_eligible_race___6 == 1 ~ 6,
      ss_eligible_race___7 == 1 ~ 7
    ),
      ## address multiplicity
      race_n = ss_eligible_race___1 + ss_eligible_race___2 + ss_eligible_race___3 + ss_eligible_race___4 + 
      ss_eligible_race___5 + ss_eligible_race___6,
    # filter(race_n > 1) |> 
    # select(study_id, ss_eligible_race___1: ss_eligible_race___7, race_n)
    race = if_else(race_n > 1, 6, race),
    race = refmt(race, racefmt),
    hisp = refmt(ss_eligible_hisp, ynfmt),
    ss_eligible_edu = refmt(ss_eligible_edu, edufmt),
    work_status_bl = refmt(work_status_bl, workfmt),
    pcp_bl = refmt(pcp_bl, ynfmt),
    health_insure = case_when(
      type_of_insurance_bl___1 + type_of_insurance_bl___2 > 0 ~ "Medicare/Medicaid",
      type_of_insurance_bl___3 + type_of_insurance_bl___4  + type_of_insurance_bl___5 + type_of_insurance_bl___6  + type_of_insurance_bl___7 > 0 ~ "Other types of insurance",
      type_of_insurance_bl___8 == 1 ~ "I am not sure",
      type_of_insurance_bl___0 == 1 ~ "None"
    ),
    health_insure = factor(health_insure, levels = c("Medicare/Medicaid", "Other types of insurance", "I am not sure", "None")),
    preg_num = case_when(
      pregnancies_bl == 0 ~ "0",
      pregnancies_bl == 1 ~ "1",
      pregnancies_bl %in% 2:3 ~ "2-3",
      pregnancies_bl == 99 ~ "Choose not to answer",
      pregnancies_bl >= 4 ~ "4+"
    ),
    sf_q1_bl = refmt(sf_q1_bl, hlth4fmt),
    # BMI
    height_cm = if_else(height_bl == 34, NA, (3 * 12 + 10 + height_bl) * 2.54),
    weight_kg = if_else(weight_bl == 999, NA, weight_bl * 0.453592),
    bmi = weight_kg / (height_cm / 100)^2
    )




# label

var_label(tmp2) <- list(
  ss_age = "Age (years)",
  race = "Race",
  hisp = "Hispanic/Latino",
  trt = "Randomization status",
  
  height_cm = "Height (cm)",
  weight_kg = "Weight (kg)",
  bmi = "Body mass index (kg/m^2)",
  
  ss_eligible_edu = "Education",
  work_status_bl = "Work status",
  pcp_bl = "Have a primary care provider",
  health_insure = "Health insurance",
  preg_num = "Number of pregnancies",
  sf_q1_bl = "Overall health in past 4 weeks (self-rated)",

  
  medcond_bl___1 = "High blood pressure",
  medcond_bl___2 = "Diabetes",
  medcond_bl___3 = "Obesity",
  medcond_bl___4 = "Memory problems",
  medcond_bl___5 = "Anxiety",
  medcond_bl___6 = "Depression",
  medcond_bl___7 = "Cancer",
  medcond_bl___8 = "Chronic pain",
  relevantsurghx_bl___1 = "Hysterectomy",
  relevantsurghx_bl___2 = "Cholecystectomy",
  relevantsurghx_bl___3 = "Surgery for pelvic organ prolapse",
  relevantsurghx_bl___4 = "Mesh sling for urinary incontinence",
  relevantsurghx_bl___5 = "Other surgery for urinary incontinence",
  relevantsurghx_bl___6 = "Surgery for bowel incontinence"
)


# demo <- tmp2 |> 
#   tbl_summary(
#     by = trt,
#     include = c(ss_age, race, hisp, height_cm, weight_kg, bmi, ss_eligible_edu, work_status_bl, pcp_bl, health_insure,
#                 preg_num, sf_q1_bl, medcond_bl___1:medcond_bl___8, relevantsurghx_bl___1:relevantsurghx_bl___6),
#   ) |> 
#   add_p() |> 
#   italicize_levels()
# 
# saveRDS(demo, "data/demo.rds")

demo <- readRDS("data/demo.rds")

demo
```

<!-- baseline symptom bother, severity, behaviors, and care seeking patterns -->

### Health behavior

Health behaviors that may impact bladder or bowel health at baseline (Sec. 2 of `baseline_survey`) are summarized by randomized arm in @tbl-base-behav.

```{r}
#| label: tbl-base-behav
#| tbl-cap: Baseline health behaviors by randomized arm.
 
## formats

# 1	Once per month or less
# 2	A few times per month
# 3	At least once per week
# 4	Several times per week
# 5	At least once per day
# 6	Several times per day
# 99	Choose not to answer
kegelfmt <- c(
  "1" = "Once per month or less",
  "2" = "A few times per month",
  "3" = "At least once per week",
  "4" = "Several times per week",
  "5" = "At least once per day",
  "6" = "Several times per day",
  "99" = "Choose not to answer"
)
# 1	Less than I should
# 2	About what I should
# 3	More than I should
# 99	Choose not to answer
fiberfmt <- c(
  "1" = "Less than I should",
  "2" = "About what I should",
  "3" = "More than I should",
  "99" = "Choose not to answer"
)
# 1	Less than I should
# 2	About what I should
# 3	More than I should
# 99	Choose not to answer
fluidfmt <- c(
  "1" = "Less than I should",
  "2" = "About what I should",
  "3" = "More than I should",
  "99" = "Choose not to answer"
)
# 0	I do not drink coffee
# 1	Less than 3 servings per week
# 2	3-6 servings per week
# 3	1 serving (12 ounces) per day
# 4	2 servings (24 ounces) per day
# 5	3 or more servings (36 ounces) per day
# 99	Choose not to answer
coffeefmt <- c(
  "0" = "I do not drink coffee",
  "1" = "Less than 3 servings per week",
  "2" = "3-6 servings per week",
  "3" = "1 serving (12 ounces) per day",
  "4" = "2 servings (24 ounces) per day",
  "5" = "3 or more servings (36 ounces) per day",
  "99" = "Choose not to answer"
)
# 0	I do not drink soda with caffeine
# 1	Less than 3 servings per week
# 2	3-6 servings per week
# 3	1 serving (12 ounces) per day
# 4	2 servings (24 ounces) per day
# 5	3 or more servings (36 ounces) per day
# 99	Choose not to answer
sodafmt <- c(
  "0" = "I do not drink soda with caffeine",
  "1" = "Less than 3 servings per week",
  "2" = "3-6 servings per week",
  "3" = "1 serving (12 ounces) per day",
  "4" = "2 servings (24 ounces) per day",
  "5" = "3 or more servings (36 ounces) per day",
  "99" = "Choose not to answer"
)
# 1	Less than 1 serving per week
# 2	1 serving per week
# 3	2-3 servings per week
# 4	4-6 servings per week
# 5	1 serving per day
# 6	More than 1 serving per day
# 99	Choose not to answer
fruitfmt <- c(
  "1" = "Less than 1 serving per week",
  "2" = "1 serving per week",
  "3" = "2-3 servings per week",
  "4" = "4-6 servings per week",
  "5" = "1 serving per day",
  "6" = "More than 1 serving per day",
  "99" = "Choose not to answer"
)
# 0	None
# 1	Less than $5
# 2	$5 - $10
# 3	$11 - $20
# 4	$21 - $30
# 5	$31 - $50
# 6	$51 - $100
# 7	$101 - $200
# 8	More than $200
# 99	Choose not to answer
moneyfmt <- c(
  "0" = "None",
  "1" = "Less than $5",
  "2" = "$5 - $10",
  "3" = "$11 - $20",
  "4" = "$21 - $30",
  "5" = "$31 - $50",
  "6" = "$51 - $100",
  "7" = "$101 - $200",
  "8" = "More than $200",
  "99" = "Choose not to answer"
)
# 1	less than 4 times per day
# 2	4-5 times
# 3	6-8 times
# 4	9-10 times
# 5	11-12 times
# 6	more than 12 times per day
# 99	Choose not to answer
voidfmt <- c(
  "1" = "less than 4 times per day",
  "2" = "4-5 times",
  "3" = "6-8 times",
  "4" = "9-10 times",
  "5" = "11-12 times",
  "6" = "more than 12 times per day",
  "99" = "Choose not to answer"
)
# 1	4 hours or more
# 2	3 hours
# 3	2 hours
# 4	1 hour
# 5	less than 1 hour
# 99	Choose not to answer
voidintervalfmt <- c(
  "1" = "4 hours or more",
  "2" = "3 hours",
  "3" = "2 hours",
  "4" = "1 hour",
  "5" = "less than 1 hour",
  "99" = "Choose not to answer"
)


tmp_behav <- tmp |> 
  select(
    study_id, rand_round_2, 
    kegel_freq_bl:voidinterval_bl) |> 
  mutate(
    trt = refmt(rand_round_2, armfmt),
    kegel_freq_bl = refmt(kegel_freq_bl, kegelfmt),
    fiber_guess_bl = refmt(fiber_guess_bl, fiberfmt),
    fluid_guess_bl = refmt(fluid_guess_bl, fluidfmt),
    freq_coffee_bl = refmt(freq_coffee_bl, coffeefmt),
    freq_soda_bl = refmt(freq_soda_bl, sodafmt),
    fruit_bl = refmt(fruit_bl, fruitfmt),
    grnsalad_bl = refmt(grnsalad_bl, fruitfmt),
    potato_bl = refmt(potato_bl, fruitfmt),
    vegetable_bl = refmt(vegetable_bl, fruitfmt),
    vegetjuice_bl = refmt(vegetjuice_bl, fruitfmt),
    vegetsoup_bl = refmt(vegetsoup_bl, fruitfmt),
    cereal_bl = refmt(cereal_bl, fruitfmt),
    wheat_bread_bl = refmt(wheat_bread_bl, fruitfmt),
    beans_bl = refmt(beans_bl, fruitfmt),
    use_liner_bl = miss99(use_liner_bl),
    use_pads_bl = miss99(use_pads_bl),
    use_depends_bl = miss99(use_depends_bl),
    incont_money_bl = refmt(incont_money_bl, moneyfmt),
    daytimevoids_bl = refmt(daytimevoids_bl, voidfmt),
    voidinterval_bl = refmt(voidinterval_bl, voidfmt)
  )

# colnames(tmp_behav)

var_label(tmp_behav) <- list(
  kegel_freq_bl = "Kegel squeezes in last 4 weeks",
  fiber_guess_bl = "Daily fiber intake",
  fluid_guess_bl = "Daily fluid intake",
  est_totalfluid_bl = "Estimated total fluid intake",
  freq_coffee_bl = "Servings of coffee last week",
  freq_soda_bl = "Servings of soda last week",
  fruit_bl = "Fruit last 4 weeks",
  grnsalad_bl = "Green salad last 4 weeks",
  potato_bl = "Potato last 4 weeks",
  vegetable_bl = "Vegetable last 4 weeks",
  vegetjuice_bl = "Vegetable juice last 4 weeks",
  vegetsoup_bl = "Vegetable soup last 4 weeks",
  cereal_bl = "Fiber cereal last 4 weeks",    
  wheat_bread_bl = "Whole wheat/rye bread last 4 weeks",
  beans_bl = "Beans last 4 weeks",
  
  usecontainprod_bl___1 =	"I use panty liners",
  usecontainprod_bl___2	= "I use pads",
  usecontainprod_bl___3	= "I use undergarments (e.g., Depends/diapers)",
  usecontainprod_bl___4	= "I use something else",
  usecontainprod_bl___5	= "I do not use anything",
  use_liner_bl = "Number of panty liners used per 24 h",
  use_pads_bl = "Number of pads used per 24 h",
  use_depends_bl = "Number of undergarments used per 24 h",
  incont_money_bl = "Money spent on managing symptoms last month",
  voidsovernight_bl = "Number of urinations overnight",
  daytimevoids_bl = "Number of urinations during daytime",
  voidinterval_bl = "Time between urinations"
)


# 
# behav <- tmp_behav |>
#   tbl_summary(by = trt,
#               include = c(kegel_freq_bl:voidinterval_bl, -usecontainprod_bl___99),
#               type = list(
#                 use_liner_bl = "continuous",
#                 use_pads_bl = "continuous",
#                 use_depends_bl = "continuous"
#               ),
#               # round continuous statistics to first decimal point
#               digits = list(
#                 all_continuous() ~ 1
#               )
#   ) |>
#   add_p() |>
#   italicize_levels()

# # save to file, read file, and print table
# saveRDS(behav, "data/behav.rds")
behav <- readRDS("data/behav.rds")
behav


```

### Bladder Symptoms

Bladder symptoms at baseline (Sec. 3 of `baseline_survey`) are summarized by randomized arm in @tbl-base-bladder.

```{r}
#| label: tbl-base-bladder
#| tbl-cap: Baseline bladder symptoms by randomized arm.

# colnames(bld_tmp)
## formats
# 0	Never
# 1	About once a week or less often
# 2	Two or three times a week
# 3	About once a day
# 4	Several times a day
# 5	All the time
# 99	Choose not to answer
iciqui_fmt <- c(
  "0" = "Never",
  "1" = "About once a week or less often",
  "2" = "Two or three times a week",
  "3" = "About once a day",
  "4" = "Several times a day",
  "5" = "All the time",
  "99" = "Choose not to answer"
)
# 0	None
# 2	A small amount
# 4	A moderate amount
# 6	A large amount
# 99	Choose not to answer
iciqui_howmuchfmt <- c(
  "0" = "None",
  "2" = "A small amount",
  "4" = "A moderate amount",
  "6" = "A large amount",
  "99" = "Choose not to answer"
)
# 1	Not at all
# 2	Somewhat
# 3	Moderately
# 4	Quite a bit
# 99	Choose not to answer
quartfmt <- c(
  "1" = "Not at all",
  "2" = "Somewhat/Slightly",
  "3" = "Moderately",
  "4" = "Quite a bit/Greatly",
  "99" = "Choose not to answer"
)
# 0	No
# 1	Yes, but it was not very helpful
# 2	Yes, and it was helpful
# 99	Choose not to answer
bld_helpfmt <- c(
  "0" = "No",
  "1" = "Yes, but not very helpful",
  "2" = "Yes, and helpful",
  "99" = "Choose not to answer"
)

refmt_quart <- function(x){
  refmt(x, quartfmt)
}


bld_tmp <- tmp |> 
  select(
    study_id, rand_round_2, 
    iciqui_leak_bl:bics_hcpnoint_bl) |> 
  mutate(
    trt = refmt(rand_round_2, armfmt),
    iciqui_leak_bl = refmt(iciqui_leak_bl, iciqui_fmt),
    iciqui_howmuch_bl = refmt(iciqui_howmuch_bl, iciqui_howmuchfmt),
    iciqui_interfer_bl = miss99(iciqui_interfer_bl),
    gse_ui1_bl = miss99(gse_ui1_bl),
    gse_ui2_bl = miss99(gse_ui2_bl),
    bladderseekhx_bl = refmt(bladderseekhx_bl, bld_helpfmt),
    across(c(pfiq_bladder_chores_bl:pfiq_bladder_frustrated_bl,
             bics_nohcp_bl:bics_hcpnoint_bl), refmt_quart)
  )
  

# lable the variables

var_label(bld_tmp) <- list(
  iciqui_leak_bl = "Leakage",
  iciqui_howmuch_bl = "Amount of leakage",
  iciqui_interfer_bl = "Leakage interferes with daily life (0-10)",

  iciqui_urineleak_bl___1 = "Urine does not leak",
  iciqui_urineleak_bl___2 = "Leaks before getting to toilet",
  iciqui_urineleak_bl___3 = "Leaks when you cough or sneeze",
  iciqui_urineleak_bl___4 = "Leaks when asleep",
  iciqui_urineleak_bl___5 = "Leaks when physically active/exercising",
  iciqui_urineleak_bl___6 = "Leaks when finished urinating and dressed",
  iciqui_urineleak_bl___7 = "Leaks for no obvious reason",
  iciqui_urineleak_bl___8 = "Leaks all the time",
  
  gse_ui1_bl = "Confidence in controlling urine (0-10)",
  gse_ui2_bl = "Confidence in preventing urine loss (0-10)",
  
  pfiq_bladder_chores_bl = "Ability to do household chores",
  pfiq_bladder_walk_bl = "Ability to walk/swim/exercise",
  pfiq_bladder_movie_bl = "Ability to go to movies/concerts",
  pfiq_bladder_travel_bl = "Ability to travel by car/bus 30min away",
  pfiq_bladder_social_bl = "Ability to socialize outside home",
  pfiq_bladder_emotion_bl = "Emotional health (nervousness, depression, etc)",
  pfiq_bladder_frustrated_bl = "Feeling frustrated",
  
  bladderseekhx_bl = "Sought help with health professionals",
  bics_nohcp_bl = "No health care practitioner to help me",
  bics_insexp_bl = "Long delays before insurance repays",
  bics_inscomp_bl = "Insurance too complicated to figure out",
  bics_csthigh_bl = "Cost of leakage evaluation too high",
  bics_notrans_bl = "No transportation to office or clinic",
  bics_waitlng_bl = "Long waiting times for appointments",
  bics_clncdist_bl = "Office/Clinic too far away",
  bics_apptfar_bl = "Appointment schedule too far ahead",
  bics_hrlimit_bl = "Office hours too limited",
  bics_examine_bl = "Don't like to be examined/asked many questions",
  bics_hcptime_bl = "Physician/nurse doesn't take time with me",
  bics_afrsrsprob_bl = "Afraid of serious problem",
  bics_afraidhcp_bl = "Afraid of health care practitioner",
  bics_hcpnoint_bl = "HCP not interested in my problem"
)

# bld <- bld_tmp |> 
#   select(-iciqui_urineleak_bl___99) |> 
#   tbl_summary(by = trt,
#               include = iciqui_leak_bl:bics_hcpnoint_bl,
#               digits = list(
#                 all_continuous() ~ 1
#                 )
#               ) |>
#   add_p() |>
#   italicize_levels()
#   
# saveRDS(bld, "data/bld.rds")
bld <- readRDS("data/bld.rds")
bld
```

### Bowel Symptoms

Bowel symptoms at baseline (Sec. 4 of `baseline_survey`) are summarized by randomized arm in @tbl-base-bowel.

```{r}
#| label: tbl-base-bowel
#| tbl-cap: Baseline bowel symptoms by randomized arm.


# colnames(bwl_tmp)
## formats
# 1	Never (less than once per month)
# 2	Rarely (about once a month)
# 3	Sometimes (2-3 times a month)
# 4	Weekly
# 5	Daily
# 99	Choose not to answer
bwl_freqfmt <- c(
  "1" = "Never (less than once per month)",
  "2" = "Rarely (about once a month)",
  "3" = "Sometimes (2-3 times a month)",
  "4" = "Weekly",
  "5" = "Daily",
  "99" = "Choose not to answer"
)
refmt_bwl_freq <- function(x){
  refmt(x, bwl_freqfmt)
}
refmt_yn <- function(x){
  refmt(x, ynfmt)
}


bwl_tmp <- tmp |> 
  select(
    study_id, rand_round_2, 
    fvq_bmconst_bl:bowelseekhx_bl) |> 
  mutate(
    trt = refmt(rand_round_2, armfmt),
    across(smis_solid_bl:sis_lifestyle_bl, refmt_bwl_freq),
    across(smis_padplug_bl:smis_deferdef_bl, refmt_yn),
    across(gse_abl1_bl:gse_abl2_bl, miss99),
    bowelseekhx_bl = refmt(bowelseekhx_bl, bld_helpfmt)
  )

var_label(bwl_tmp) <- list(
  smis_solid_bl = "Solid stool incontinence",
  smis_liquid_bl = "Liquid stool incontinence",
  smis_gas_bl = "Gas incontinence",
  sis_lifestyle_bl = "Bowel symptoms affecting lifestyle",
  smis_padplug_bl = "Use of pads/plugs",
  smis_meds_bl = "Use of medications",
  smis_deferdef_bl = "Have to rush to toilet when having urge",
  
  gse_abl1_bl = "Confidence in controlling bowel (0-10)",
  gse_abl2_bl = "Confidence in preventing bowel loss (0-10)",
  bowelseekhx_bl = "Sought help with health professionals"
)

# bwl <- bwl_tmp |>
#   tbl_summary(by = trt,
#               include = smis_solid_bl:bowelseekhx_bl,
#               digits = list(
#                 all_continuous() ~ 1
#               )
#   )
# #
# saveRDS(bwl, "data/bwl.rds")
bwl <- readRDS("data/bwl.rds")
bwl
```
